\section{Background}

\subsection{Congestion Control general Information}

Congestion Control describes all algorithms, that are used to control how much packet a sender is sending. 
The main focus of Congestion Control lies on TCP connections, because there a low latency and high throughtput a wanted, while the packet loss should be zero.
In \cite{JainsCongestionControl} describes the main reasons and challanges for congestion control algorithms that have not changed since.
The author identifies three main hardware limits of a bottleneck router, which are buffer, transmission speed and speed of CPU of the bottleneck router.
If a router is upgraded, but not proportionaly equal in all three at the same time, it will cause problems and actually limit the capacity of the adjusted router.
Therefore, Congestion Control algorithms are necessary, because Hardware has its limits.

\subsubsection{Measuring Indices}

When a Congestion Control Algorithm is developed, its founders want to know, if there idea is good or not. 
To determine a good Congestion Control algorithm there are a few indices.
One of them is Jains fairness Index and it measures the fairness of an congestion control algorithm in respect to how fair flows share the bottleneck resources.
Jains Index is a number between 0 and 1 where its value describes the amount in percentage of users in who get a fair share of the resources. 
So 1 means 100\% of the users get a fair share\cite{JainsIndex}.

\subsubsection{Types of Congestion Controls}

loss-Based

delay-Based

congestion-Based

\subsubsection{Places of deployment}

Short distance networks

long distance networks

data center

satelite links

small buffer at Bottleneck

large buffer at Bottleneck

\subsection{TCP Cubic}

When the internet startet to grow and it became evident, that it will be more high speed and long distance network, older TCP Congestion Control Algorithm have less scalibility to tackle the challenges of the internet\cite{TCPCUBIC}.
The authors of TCP Cubic wanted to build a stable and scalable TCP version that can handle the new challanges of the internet.
The basic idea behind TCP Cubic is that it uses a Cubic congestion window function\cite{TCPCUBIC}.
Most other Congestion Control Algorithms at that time increased their packet rate only by one packet per RTT, which could lead to a very slow start and before a sender would start fully using its network resources, it could take hours.
The cubic function starts to increase its packet rate very fast and then slows down in after some time, in order to not heavily overstep the bottleneck threshold.
\cite{TCPCUBIC}
It detects the bottlenecks limit by watching for packets loss. 
This means, when the packet loss increases, then the bottleneck is not able to handle more packets and TCP Cubic knows it has reached the limit.
\cite{TCPCUBIC}


\subsection{TCP Vegas}

The authors of TCP Vegas wanted to improv the existing TCP Reno and wanted to introduce a way on how to increase throughtput and lower packet loss.
They figured out, that loss-based Congestion COntrol Algorithms create unnecessary packet losses and these lost packets then need to be retransmitted.
Moreover, they realized, that with measuring the RTT of a packet, they can get more information out of it.
\cite{TCPVEGAS}


\subsection{Fast TCP}

Like the authors of TCP Cubic the authors of FAST TCP recognized that the internet grows more and more and is more and more a long distance network. 
However, other than \cite{TCPCUBIC}, the authors in \cite{FASTTCP} focused more on the speed of the flows.
FAST TCP is a delay-based Congestion Control Algorithm and targets to have an extremly low loss probability.
Moreover, the authors do not want the binary classification that other Congestion Control Algorithms have, because it can result to oscilations in the congestion window.
That is why they decided to use queuing-dely as their primary measure of congestion\cite{FASTTCP}.
It is possible to understand more about the state of the network, if the measurement is more than just packet arrived or not, because if you measure the RTT, it is possible to see, when the networks bottleneck gets trouble handling the traffic.
Furthermore, the authors of FAST TCP wanted the congestion window not to be iterativly increased, but more flexible.
With other words, the congestion window in FAST TCP can change depending on how far away from the threshold it is.
\cite{FASTTCP}
